Scaffolder - Software for \change{Reproducible}{Manual} Genome Scaffolding.

### 2011-08-13 src/article.tex
Update version dependency requirements
Add link to scaffolder getting started

Scaffolder provides a standardised set of Ruby classes and methods (API) for
interacting with the scaffold. This allows Scaffolder to be integrated into
existing genomics workflows or used with Ruby build tools such as Rake. In
addition Scaffolder provides a command line interface (CLI) to validate the
scaffold file and build the draft super sequence. The Scaffolder CLI behaves
as a standard Unix tool and returns appropriate exit codes and manual pages.
The use of both these Scaffolder interfaces is outlined in detail on the
scaffolder website (\scaffolder). \pb

@@

  \begin{description}
    \item[Project name:] Scaffolder v0.4.1, Scaffolder Tools v0.1.2
    \item[Project home page:] \scaffolder
    \item[Operating system:] Platform Independent. Tested on Mac OS X and
    Ubuntu.
    \item[Programming language:] Ruby
    \item[Other requirements:] \change{RubyGems}{RubyGems package management
    software and the following libraries: BioRuby and confligliere. A full
    list of development dependencies can be found in the Gemfile in the base
    directory of each project.}
    \item[License:] MIT
    \item[Any restrictions to use by non-academics:] None
  \end{description}

>>>>

Scaffolder provides a standardised set of Ruby classes and methods (API) for
interacting with the scaffold. This allows Scaffolder to be integrated into
existing genomics workflows or used with Ruby build tools such as Rake. In
addition Scaffolder provides a command line interface (CLI) to validate the
scaffold file and build the draft super sequence. The Scaffolder CLI behaves
as a standard Unix tool and returns appropriate exit codes and manual pages.
The use of both these Scaffolder interfaces is outlined in detail on the
scaffolder website (\scaffolder). \add{This website also contains a ``getting
started'' guide which introduces using Scaffolder.} \pb

@@

  \begin{description}
    \item[Project name:] Scaffolder v0.4.\change{1}{4}, Scaffolder Tools
    v0.1.\change{2}{3}
    \item[Project home page:] \scaffolder
    \item[Operating system:] Platform Independent. Tested on Mac OS X and
    Ubuntu.
    \item[Programming language:] Ruby \add{1.8.7 or 1.9.2}
    \item[Other requirements:] \change{RubyGems}{RubyGems package management
    software and the following libraries: BioRuby \add{1.4.x}, confligliere
    \add{0.1.x}\add{, ronn 0.7.x}. A full list of development dependencies
    can be found in the Gemfile in the base directory of each project.}
    \item[License:] MIT
    \item[Any restrictions to use by non-academics:] None
  \end{description}
